### 2019-12-13 README.Rmd
changed to sfzoner

# sfquadrants

@@

The goal of sfquadrants is to ...

@@

You can install the released version of sfquadrants from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sfquadrants")
```

@@

``` r
# install.packages("devtools")
devtools::install_github("robinlovelace/sfquadrants")
```

>>>>

# sfzoner

@@

The goal of sfzoner is to ...

@@

You can install the released version of sfzoner from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("sfzoner")
```

@@

``` r
# install.packages("devtools")
devtools::install_github("robinlovelace/sfzoner")
```
